---
title: "project graph 2"
author: "Zhipeng Chen"
date: "2022/3/13"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(mdsr)
library(readxl)
library(data.table)
library(scales)
library(repr)
library(forcats)

Europe_Power_Sector_2020 <- read_excel("C:/Users/12694/OneDrive/Desktop/Spring 2022/STAT 4380 data science/midterm project/Data-file-Europe-Power-Sector-2020.xlsx", 
    sheet = "Pivot, % of production", col_types = c("numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric"), skip = 3)

```

# problem 1: I found data is very hard to process. I can not categorize the different types of energy since they are in differet columns

## 1. drop columns with all NAs 
## 2. convert data frame to data table in order to use `melt()`
## 3. Reshape R dataframes wide-to-long with melt

```{r}
EU_power2 <- Europe_Power_Sector_2020 %>%
   select(-"Demand", -"Production", -"Net imports") %>%
    dplyr::rename(`Fossil fuels` = Fossil)


setDT(EU_power2)
class(EU_power2)

EU_reshaped <- melt(data = EU_power2,
        id.vars = c("Row Labels"),
        variable.name = "type of energy",
        value.name = "Sum of Share of production (%)")
```

#problem 2: combining line graph part and bar graph part in one chart

##set two different datasets for two graphs in the same charts
##make two lines based on different type of energy and set specific color for both
##make good linetype
##good points
##title and subtitle
##position, size and shapes/colors of legends/remove the legend title
##remove x and y axis labels
##size, limit and breaks of x and y labels / convert y axis labels to percents
##change the color of plot and panel backgound/
##remove all vertical gridlines and minor horizontal gridlines/ change the color of gridlines
##set ticks color and size and length
##make stacked bar graph/ changing stacked order from 
##
##let stacked bar chart bw shown below the line graph 


#Difficulty
##cannot make specific color for individual word in the title
##cannot make legend shape rounded tectangle
##cannot make line more smoothier while the line crosses dots
##cannot make it in right order for legends from different datasets

```{r line_bar_and_format}

data_line <- EU_reshaped %>%
    filter(`type of energy` == "Fossil fuels" |  `type of energy` =="Renewables") 

data_bar <- EU_reshaped %>%
    filter(`type of energy` == "Bioenergy" | `type of energy` =="Hydro" |
           `type of energy` == "Other renewables" | `type of energy` =="Solar" | `type of energy` == "Wind")

    as.factor(data_bar$`type of energy`)
    class(data_bar$`type of energy`)


    
ggplot() +
    geom_bar(data = data_bar, aes(x = `Row Labels`, 
                                  y = `Sum of Share of production (%)`, 
                                  fill = factor(`type of energy`, 
                                                levels = c("Wind", "Solar", "Other renewables", "Hydro", "Bioenergy"))), stat = "identity") +
    geom_line(data = data_line, aes(x = `Row Labels`, 
                                    y = `Sum of Share of production (%)`, 
                                    color = `type of energy`), 
              size = 2.5) +
    geom_point(data = data_line, aes(x = `Row Labels`, 
                                     y = `Sum of Share of production (%)`,
                                     color = `type of energy`),
               size = 4.25) +
    labs(title = "Renewables growth driven by wind and solar", 
         subtitle = "% share of electricity production in EU-27",
         caption = "Europe's Power Sector in 2020, published by Ember and Agora Energiewende on 25th Januart 2021") +
    theme(plot.title = element_text(size = 24.5, face = "bold"),
        plot.subtitle = element_text(size = 17.5),
        plot.caption = element_text(color = "#666666", size = 15, hjust = 0), 
        plot.background = element_rect(fill = "#F0F0F0"),
        panel.background = element_rect(color = "#F0F0F0", fill = "#F0F0F0"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major=element_line(colour="#AFB3B3", size = 1),
        panel.grid.minor=element_blank(),
        legend.position = "top",
        legend.title = element_blank(),
        legend.key=element_blank(),
        legend.background = element_rect(color = "#F0F0F0", fill = "#F0F0F0"),
        legend.text = element_text(size = 15),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 13.5, color = "#666666"),
        axis.text.y = element_text(size = 15, color = "#666666"),
        axis.ticks=element_line(size = 1, color = "#AFB3B3"),
        axis.ticks.length=unit(.25, "cm")) +
    guides(color = guide_legend(override.aes=list(shape = 15,
                                                  linetype = 0))) +
    scale_x_continuous(breaks=seq(2010, 2020, by = 1)) +
    scale_y_continuous(limit = c(0, 50),
                       breaks= seq(0, 50, by = 10),
                       label = percent_format(accuracy = 1, scale = 1),
                       expand = c(0, NA)) +
    scale_color_manual(values = c("Fossil fuels" = "#000033","Renewables" = "#6DB562")) +
    scale_fill_manual(values = c("Bioenergy" = "#919191", "Hydro" = "#00E5EE", "Other renewables" = "#EE82EE", "Solar" = "#FFD700", "Wind" = "#1874CD"))
    
    
    

                    
```







